% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  ignorenonframetext,
]{beamer}
\usepackage{pgfpages}
\setbeamertemplate{caption}[numbered]
\setbeamertemplate{caption label separator}{: }
\setbeamercolor{caption name}{fg=normal text.fg}
\beamertemplatenavigationsymbolsempty
% Prevent slide breaks in the middle of a paragraph
\widowpenalties 1 10000
\raggedbottom
\setbeamertemplate{part page}{
  \centering
  \begin{beamercolorbox}[sep=16pt,center]{part title}
    \usebeamerfont{part title}\insertpart\par
  \end{beamercolorbox}
}
\setbeamertemplate{section page}{
  \centering
  \begin{beamercolorbox}[sep=12pt,center]{section title}
    \usebeamerfont{section title}\insertsection\par
  \end{beamercolorbox}
}
\setbeamertemplate{subsection page}{
  \centering
  \begin{beamercolorbox}[sep=8pt,center]{subsection title}
    \usebeamerfont{subsection title}\insertsubsection\par
  \end{beamercolorbox}
}
\AtBeginPart{
  \frame{\partpage}
}
\AtBeginSection{
  \ifbibliography
  \else
    \frame{\sectionpage}
  \fi
}
\AtBeginSubsection{
  \frame{\subsectionpage}
}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\newif\ifbibliography
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
\usepackage{caption}
% Make caption package work with longtable
\makeatletter
\def\fnum@table{\tablename~\thetable}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Stakeholder Identification Guide},
  pdfauthor={Based on Course Materials \& Workwear 4U Scenario},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Stakeholder Identification Guide}
\subtitle{For Workwear 4U Coursework Tasks}
\author{Based on Course Materials \& Workwear 4U Scenario}
\date{2025-06-19}

\begin{document}
\frame{\titlepage}

\begin{frame}{Our Goal: Identify 4 Key Stakeholders}
\phantomsection\label{our-goal-identify-4-key-stakeholders}
\textbf{What we need to produce:}

\begin{itemize}
\tightlist
\item
  Stakeholder Register with 4 stakeholders (Task 1 - 20 marks)
\item
  Each stakeholder must connect to our use cases and XP stories
\end{itemize}

\textbf{Our specific deliverables:}

\begin{itemize}
\tightlist
\item
  \textbf{Use Cases:} ``Place Order from retail shop'' \& ``Generate
  Delivery Note''
\item
  \textbf{XP Stories:} ``Receive Container delivery'' \& ``Generate
  monthly invoice''
\end{itemize}

\textbf{Method:} Work backwards from these deliverables to find
stakeholders

\emph{Source: CW Task 1 Specification \textbar{} Appendix A Template}
\end{frame}

\begin{frame}{Step 1: Extract Stakeholders from Use Cases}
\phantomsection\label{step-1-extract-stakeholders-from-use-cases}
\textbf{Use Case 1: ``Place Order from retail shop''}

\begin{itemize}
\tightlist
\item
  Who places the order?
\item
  Who receives the order?
\item
  Who processes the order?
\end{itemize}

\textbf{Use Case 2: ``Generate Delivery Note for Retail Outlet''}

\begin{itemize}
\tightlist
\item
  Who generates the note?
\item
  Who receives the delivery?
\item
  Who supplies the items?
\end{itemize}

\emph{Source: CW Task 2 Specifications \textbar{} FSE\_Lecture
Slides\_Week 5 2425.pdf}
\end{frame}

\begin{frame}{Step 1: Suggested Answers}
\phantomsection\label{step-1-suggested-answers}
\textbf{Use Case 1 Suggestions:}

\begin{itemize}
\tightlist
\item
  Who places the order? → \textbf{Retail Shop Staff/Manager}
\item
  Who receives the order? → \textbf{Head Office Administrator}
\item
  Who processes the order? → \textbf{Supplier} or \textbf{Warehouse
  Staff}
\end{itemize}

\textbf{Use Case 2 Suggestions:}

\begin{itemize}
\tightlist
\item
  Who generates the note? → \textbf{Warehouse Manager}
\item
  Who receives the delivery? → \textbf{Retail Shop Staff}
\item
  Who supplies the items? → \textbf{Chinese Supplier}
\end{itemize}

\emph{These are suggestions - discuss and decide what makes most sense
for our analysis}
\end{frame}

\begin{frame}{Step 2: Extract Stakeholders from XP Stories}
\phantomsection\label{step-2-extract-stakeholders-from-xp-stories}
\textbf{XP Story 1: ``Receive Container delivery from Chinese
Supplier''}

\begin{itemize}
\tightlist
\item
  Who benefits from this capability?
\item
  Who's directly involved in the process?
\end{itemize}

\textbf{XP Story 2: ``Generate monthly invoice for Trade Customers''}

\begin{itemize}
\tightlist
\item
  Who benefits from getting clear invoices?
\item
  Who would generate these invoices?
\item
  Who receives and pays the invoices?
\end{itemize}

\emph{Source: CW Task 3 Specifications \textbar{} FSE\_Lecture
Slides\_Week 3 2425(1).pdf}
\end{frame}

\begin{frame}{Step 2: Suggested Answers}
\phantomsection\label{step-2-suggested-answers}
\textbf{XP Story 1 Suggestions:}

\begin{itemize}
\tightlist
\item
  Who benefits? → \textbf{Warehouse Manager} (receives goods)
\item
  Who's involved? → \textbf{Chinese Supplier}, \textbf{Shipping Company}
\end{itemize}

\textbf{XP Story 2 Suggestions:}

\begin{itemize}
\tightlist
\item
  Who benefits? → \textbf{Trade Customers} (get clear billing)
\item
  Who generates? → \textbf{Head Office Administrator}
\item
  Who pays? → \textbf{Trade Customers}
\end{itemize}

\emph{These are suggestions - consider what other stakeholders might be
involved}
\end{frame}

\begin{frame}{Step 3: Map to Workwear 4U Scenario}
\phantomsection\label{step-3-map-to-workwear-4u-scenario}
\textbf{From the scenario, identify specific roles:}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\linewidth - 4\tabcolsep) * \real{0.2609}}
  >{\raggedright\arraybackslash}p{(\linewidth - 4\tabcolsep) * \real{0.4348}}
  >{\raggedright\arraybackslash}p{(\linewidth - 4\tabcolsep) * \real{0.3043}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Stakeholder Type
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Specific Role in Workwear 4U
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Key Responsibilities
\end{minipage} \\
\midrule\noalign{}
\endhead
\textbf{Internal Staff} & Head Office Administrator & Manual order
processing, supplier contact \\
\textbf{Internal Staff} & Warehouse Manager & Container unpacking, stock
organisation \\
\textbf{Internal Staff} & Retail Branch Manager & Customer orders, stock
requests \\
\textbf{External} & Chinese Supplier & Container shipments, specialist
garments \\
\textbf{External} & Trade Customers & Regular bulk orders, account
management \\
\textbf{External} & UK Suppliers & Direct shop deliveries \\
\bottomrule\noalign{}
\end{longtable}

\emph{Source: CW Scenario Description (pages 3-5)}
\end{frame}

\begin{frame}{Step 4: Select Our 4 Most Important Stakeholders}
\phantomsection\label{step-4-select-our-4-most-important-stakeholders}
\textbf{Selection Criteria:}

\begin{enumerate}
\tightlist
\item
  \textbf{Frequency:} Appears in multiple use cases/stories
\item
  \textbf{High Impact:} Directly affected by new system
\item
  \textbf{High Influence:} Can make or break the project
\item
  \textbf{Business Importance:} Critical to Workwear 4U's success
\end{enumerate}

\textbf{Our Task:} From our Step 1-3 analysis, count how often each
stakeholder appears, then apply business judgment.
\end{frame}

\begin{frame}{Step 4: Systematic Analysis Results}
\phantomsection\label{step-4-systematic-analysis-results}
\textbf{Most Frequent Stakeholders (from our analysis):}

\begin{enumerate}
\tightlist
\item
  \textbf{Head Office Administrator} (Use Case 1 + XP Story 2)
\item
  \textbf{Retail Shop Staff/Manager} (Both Use Cases)\\
\item
  \textbf{Warehouse Manager} (Use Case 2 + XP Story 1)
\item
  \textbf{Chinese Supplier} (Use Case 2 + XP Story 1)
\end{enumerate}

\textbf{Alternative Business-Focused Selection:}

\begin{itemize}
\tightlist
\item
  Replace \textbf{Chinese Supplier} with \textbf{Trade Customers}
  (revenue importance)
\item
  Or replace with \textbf{UK Suppliers} (volume of transactions)
\end{itemize}

\emph{The systematic analysis gives you a starting point - apply
business judgment for final selection}
\end{frame}

\begin{frame}{Step 5: Complete the Stakeholder Register}
\phantomsection\label{step-5-complete-the-stakeholder-register}
\textbf{For each of our 4 stakeholders, fill out:}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\linewidth - 2\tabcolsep) * \real{0.1667}}
  >{\raggedright\arraybackslash}p{(\linewidth - 2\tabcolsep) * \real{0.8333}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Field
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Example: Head Office Administrator
\end{minipage} \\
\midrule\noalign{}
\endhead
\textbf{Full Name} & Head Office Administrator \\
\textbf{Job Role} & Order Processing Coordinator \\
\textbf{Responsibilities} & Manual order entry, supplier
communication \\
\textbf{System Needs} & Automated order processing, real-time stock
data \\
\textbf{Power/Interest} & High/High (manages all orders) \\
\textbf{Management Strategy} & Involve in all design decisions, regular
feedback \\
\bottomrule\noalign{}
\end{longtable}

\emph{Source: CW Appendix A Template}
\end{frame}

\begin{frame}{Validation: Connect Back to Deliverables}
\phantomsection\label{validation-connect-back-to-deliverables}
\textbf{Check our 4 stakeholders against:}

✓ \textbf{Frequency Count:} Do they appear most often in our analysis?\\
✓ \textbf{Use Case Actors:} Do they appear in our use case diagrams?\\
✓ \textbf{XP Story Value:} Do they benefit from the user stories?\\
✓ \textbf{System Impact:} Will the new system change how they work?\\
✓ \textbf{Business Justification:} Can you explain why you chose them
over others?

\textbf{Remember:} Multiple valid selections are possible - justify our
choices with evidence from the analysis.

\emph{Source: Requirements Traceability \textbar{} FSE\_Lecture
Slides\_Week 4 2425(1).pdf}
\end{frame}

\begin{frame}{Power/Interest Analysis}
\phantomsection\label{powerinterest-analysis}
\textbf{Power = Ability to influence the project} \textbf{Interest = How
much the system affects them}

\textbf{For each of our 4 stakeholders, assess:}

\begin{itemize}
\tightlist
\item
  What level of power do they have? (High/Medium/Low)
\item
  What level of interest do they have? (High/Medium/Low)
\item
  What management strategy follows from this?
\end{itemize}

\emph{Source: CW Appendix A \textbar{} Project Management Framework}
\end{frame}

\begin{frame}{Power/Interest: Example Assessments}
\phantomsection\label{powerinterest-example-assessments}
\textbf{Based on systematic analysis (most frequent stakeholders):}

\begin{itemize}
\tightlist
\item
  \textbf{Head Office Administrator:} High Power, High Interest (manages
  all orders)
\item
  \textbf{Retail Shop Staff/Manager:} Medium Power, High Interest (daily
  system users)
\item
  \textbf{Warehouse Manager:} Medium Power, High Interest (container
  operations)
\item
  \textbf{Chinese Supplier:} Low Power, Medium Interest (external but
  important supplier)
\end{itemize}

\textbf{Alternative business-focused example:}

\begin{itemize}
\tightlist
\item
  Replace \textbf{Chinese Supplier} with \textbf{Trade Customers:} High
  Power, Medium Interest (major revenue but external users)
\end{itemize}

\textbf{Management Strategy:} High Power = Keep satisfied, High Interest
= Keep informed

\emph{Our power/interest analysis should match our chosen 4
stakeholders}
\end{frame}

\begin{frame}{Final Checklist}
\phantomsection\label{final-checklist}
\textbf{Before submitting our stakeholder register:}

✓ Exactly 4 stakeholders identified\\
✓ Each connects to at least one use case or XP story\\
✓ Selection justified by systematic analysis (frequency + business
importance)\\
✓ Clear, specific role descriptions (not generic)\\
✓ Realistic power/interest assessments for our chosen stakeholders\\
✓ Practical management strategies\\
✓ Follows Appendix A template exactly

\textbf{Remember:} Different people / groups may select different
stakeholders - focus on strong justification and systematic approach.

\emph{Source: CW Task 1 Marking Criteria}
\end{frame}

\end{document}
